Resonant Scattering in a Uniform Sphere with Large Optical Depth

### 2020-12-16 ms.tex
Revised section on Dijkstra derivation

% TODO: (Connor) Fill out the rest of this paragraph and include equations
Rewriting Eq. C17 from \citet{2006ApJ...649...14D} in our notation, a comparison can be made with the surface flux derived from their closed-form solution, Eq. \ref{eq:H0surf}. Under the two-stream approximation, it is expected that the boundary condition in Eq. \ref{eq:bc} hold true if the solutions are consistent.

@@

>>>>

@@

% TODO: (Connor) Fill out the rest of this paragraph and include equations
To characterize the internal consistency of the solution in \citet{2006ApJ...649...14D}, the approximation made in their Eq. C13 is checked to see if it yields a surface flux satisfying Eq. \ref{eq:bc}. Beginning with their Eq. C12, the surface flux is derived and compared with the total emerging flux density at the surface of the sphere (Eq. C17). Under the two-stream approximation, it is expected that the surface boundary condition $J=\sqrt{3}H$ hold true if the solutions are consistent.

TODO: If the solutions end up being consistent, their prescription works better than one would expect, seeing as they started with a $J=0$ boundary condition and arrived at $J=\sqrt{3}H$ through their eigenvalue approximation. If the solutions are not consistent, then their emerging spectrum is inaccurate under their assumptions.
